
PR3: TRABAJO GRUPAL 
LINEAS:
-Jimena Felipe, 20180648 (13-257)
-Rafael Tang, (260-590)
-Adriana Ramos, (593-873)
-Manuel Mayaute, (877-1140)
```{r}
Lcovid="https://raw.githubusercontent.com/rafaeltang/EAP-2-ARCHIVOS/master/oficial.csv"
covid=read.csv(Lcovid,stringsAsFactors = F)
```

JIMENA FELIPE
VARIABLE:Domestic general government health expenditure
ANALISIS UNIVARIADO
```{r}
summary(covid$Domestic_general_government_health_expenditure, na.rm = T)
```

```{r}
sd(covid$Domestic_general_government_health_expenditure, na.rm = T)
var(covid$Domestic_general_government_health_expenditure, na.rm = T)
```
ANÁLISIS BIVARIADO:
Domestic general government health expenditure con:
1. CASES 
```{r}
cor.test(x = covid$Domestic_general_government_health_expenditure, y = covid$cases, method = "pearson", use="pairwise.complete.obs")
```

```{r}
plot(covid$Domestic_general_government_health_expenditure, covid$cases, 
     xlab="Domestic general government health expenditure", 
     ylab="Cases") 
```
2. DEADS
```{r}
cor.test(x = covid$Domestic_general_government_health_expenditure, y = covid$deads, method = "pearson")
```

```{r}
plot(covid$Domestic_general_government_health_expenditure, covid$deads, 
     xlab="Domestic general government health expenditure", 
     ylab="Deads")
```

3. MORTALITY
```{r}
cor.test(x = covid$Domestic_general_government_health_expenditure, y = covid$mortality, method = "pearson")
```

```{r}
plot(covid$Domestic_general_government_health_expenditure, covid$mortality, 
     xlab="Domestic general government health expenditure", 
     ylab="Mortality")
```

4.DEADS PER 100K
```{r}
cor.test(x = covid$Domestic_general_government_health_expenditure, y = covid$deadsPER100k, method = "pearson")
```
```{r}
plot(covid$deadsPER100k, covid$Domestic_general_government_health_expenditure, 
     xlab="Domestic general government health expenditure", 
     ylab="Deads per 100k")
```
5. CASES PER 100K
```{r}
cor.test(x = covid$Domestic_general_government_health_expenditure, y = covid$casesPER100k, method = "pearson")
```
```{r}
plot(covid$Domestic_general_government_health_expenditure, covid$casesPER100k, 
     xlab="Domestic general government health expenditure", 
     ylab="Cases per 100k")
```


VARIABLE: Current health expenditure 
ANALISIS UNIVARIADO 
```{r}
summary(covid$Current_health_expenditure)
```

ANALISIS BIVARIADO
Current health expenditure con:

1. CASES 
```{r}
cor.test(x = covid$Current_health_expenditure, y = covid$cases, method = "pearson")
```
```{r}
plot(covid$Current_health_expenditure, covid$cases, 
     xlab="Current health expenditure", 
     ylab="Cases")
```
2. DEADS
```{r}
cor.test(x = covid$Current_health_expenditure, y = covid$deads, method = "pearson")
```

```{r}
plot(covid$Current_health_expenditure, covid$deads, 
     xlab="Current health expenditure", 
     ylab="Deads")
```

3. MORTALITY
```{r}
cor.test(x = covid$Current_health_expenditure, y = covid$mortality, method = "pearson")
```

```{r}
plot(covid$Current_health_expenditure, covid$mortality, 
     xlab="Current health expenditure", 
     ylab="Mortality")
```

4.DEADS PER 100K
```{r}
cor.test(x = covid$Current_health_expenditure, y = covid$deadsPER100k, method = "pearson")
```
```{r}
plot(covid$Current_health_expenditure, covid$deadsPER100k, 
     xlab="Current health expenditure", 
     ylab="Deads per 100k")
```
5. CASES PER 100K
```{r}
cor.test(x = covid$Current_health_expenditure, y = covid$casesPER100k, method = "pearson")
```
```{r}
plot(covid$Current_health_expenditure, covid$casesPER100k, 
     xlab="Current health expenditure", 
     ylab="Cases per 100k")
```



VARIABLE: Out of pocket health expenditure 
ANALISIS UNIVARIADO 
```{r}
summary(covid$Out_of_pocket_health_expenditure)
```

ANALISIS BIVARIADO
Out of pocket health expenditure con:

1. CASES 
```{r}
cor.test(x = covid$Out_of_pocket_health_expenditure, y = covid$cases, method = "pearson")
```
```{r}
plot(covid$Out_of_pocket_health_expenditure, covid$cases, 
     xlab="Out of pocket health expenditure", 
     ylab="Cases")
```
2. DEADS
```{r}
cor.test(x = covid$Out_of_pocket_health_expenditure, y = covid$deads, method = "pearson")
```

```{r}
plot(covid$Out_of_pocket_health_expenditure, covid$deads, 
     xlab="Out of pocket health expenditure", 
     ylab="Deads")
```

3. MORTALITY
```{r}
cor.test(x = covid$Out_of_pocket_health_expenditure, y = covid$mortality, method = "pearson")
```

```{r}
plot(covid$Out_of_pocket_health_expenditure, covid$mortality, 
     xlab="Out of pocket health expenditure", 
     ylab="Mortality")
```

4.DEADS PER 100K
```{r}
cor.test(x = covid$Out_of_pocket_health_expenditure, y = covid$deadsPER100k, method = "pearson")
```
```{r}
plot(covid$Out_of_pocket_health_expenditure, covid$deadsPER100k, 
     xlab="Out of pocket health expenditure", 
     ylab="Deads per 100k")
```
5. CASES PER 100K
```{r}
cor.test(x = covid$Out_of_pocket_health_expenditure, y = covid$casesPER100k, method = "pearson")
```
```{r}
plot(covid$Out_of_pocket_health_expenditure, covid$casesPER100k, 
     xlab="Out of pocket health expenditure", 
     ylab="Cases per 100k")
```



VARIABLE: UHC service coverage index 
ANALISIS UNIVARIADO 
```{r}
summary(covid$UHC_service_coverage_index)
```

ANALISIS BIVARIADO
UHC service coverage index con:

1. CASES 
```{r}
cor.test(x = covid$UHC_service_coverage_index, y = covid$cases, method = "pearson")
```
```{r}
plot(covid$UHC_service_coverage_index, covid$cases, 
     xlab="UHC service coverage index", 
     ylab="Cases")
```
2. DEADS
```{r}
cor.test(x = covid$UHC_service_coverage_index, y = covid$deads, method = "pearson")
```

```{r}
plot(covid$UHC_service_coverage_index, covid$deads, 
     xlab="UHC service coverage index", 
     ylab="Deads")
```

3. MORTALITY
```{r}
cor.test(x = covid$UHC_service_coverage_index, y = covid$mortality, method = "pearson")
```

```{r}
plot(covid$UHC_service_coverage_index, covid$mortality, 
     xlab="UHC service coverage index", 
     ylab="Mortality")
```

4.DEADS PER 100K
```{r}
cor.test(x = covid$UHC_service_coverage_index, y = covid$deadsPER100k, method = "pearson")
```
```{r}
plot(covid$UHC_service_coverage_index, covid$deadsPER100k, 
     xlab="UHC service coverage index", 
     ylab="Deads per 100k")
```
5. CASES PER 100K
```{r}
cor.test(x = covid$UHC_service_coverage_index, y = covid$casesPER100k, method = "pearson")
```
```{r}
plot(covid$UHC_service_coverage_index, covid$casesPER100k, 
     xlab="UHC service coverage index", 
     ylab="Cases per 100k")
```


RAFAEL TANG

VARIABLE: Gasto gubernamental en salud
ANALISIS UNIVARIADO
```{r}
summary(covid$GovernmentHealthExp.P.C)
```

ANALSIS BIVARIADO

1.CASES
```{r}
cor.test(x = covid$GovernmentHealthExp.P.C, y = covid$cases, method = "pearson")
```

```{r}
plot(covid$cases, covid$GovernmentHealthExp.P.C, 
     xlab="Government health expenditure", 
     ylab="Cases")
```

2.DEADS
```{r}
cor.test(x = covid$GovernmentHealthExp.P.C, y = covid$deads, method = "pearson")
```

```{r}
plot(covid$GovernmentHealthExp.P.C, covid$deads, 
     xlab="Government health expenditure", 
     ylab="Deads")
```

3.MORTALITY
```{r}
cor.test(x = covid$GovernmentHealthExp.P.C, y = covid$mortality, method = "pearson")
```

```{r}
plot(covid$GovernmentHealthExp.P.C, covid$mortality, 
     xlab="Government health expenditure", 
     ylab="mortality")
```


4.DEADS PER 100K
```{r}
cor.test(x = covid$Domestic_general_government_health_expenditure, y = covid$deadsPER100k, method = "pearson")
```

```{r}
plot(covid$deadsPER100k, covid$GovernmentHealthExp.P.C, 
     xlab="Government health expenditure", 
     ylab="Deads per 100k")
```

5. CASES PER 100K
```{r}
cor.test(x = covid$GovernmentHealthExp.P.C, y = covid$casesPER100k, method = "pearson")
```

```{r}
plot(covid$GovernmentHealthExp.P.C, covid$casesPER100k, 
     xlab="Government health expenditure", 
     ylab="Cases per 100k")
```



#VARIABLE: Revenue-Ingresos
ANALISIS UNIVARIADO
```{r}
summary(covid$Revenue)
```

ANALSIS BIVARIADO

1.CASES
```{r}
cor.test(x = covid$Revenue, y = covid$cases, method = "pearson")
```

```{r}
plot(covid$cases, covid$Revenue, 
     xlab="Revenue", 
     ylab="Cases")
```

2.DEADS
```{r}
cor.test(x = covid$Revenue, y = covid$deads, method = "pearson")
```

```{r}
plot(covid$GovernmentHealthExp.P.C, covid$deads, 
     xlab="Revenue", 
     ylab="Deads")
```

3.MORTALITY
```{r}
cor.test(x = covid$Revenue, y = covid$mortality, method = "pearson")
```

```{r}
plot(covid$Revenue, covid$mortality, 
     xlab="Revenue", 
     ylab="mortality")
```


4.DEADS PER 100K
```{r}
cor.test(x = covid$Revenue, y = covid$deadsPER100k, method = "pearson")
```

```{r}
plot(covid$deadsPER100k, covid$GovernmentHealthExp.P.C, 
     xlab="Revenue", 
     ylab="Deads per 100k")
```

5. CASES PER 100K
```{r}
cor.test(x = covid$Revenue, y = covid$casesPER100k, method = "pearson")
```

```{r}
plot(covid$Revenue, covid$casesPER100k, 
     xlab="Revenue", 
     ylab="Cases per 100k")
```



#VARIABLE: Expenditure-gasto


ANALISIS UNIVARIADO
```{r}
summary(covid$Expenditure)
```

ANALSIS BIVARIADO

1.CASES
```{r}
cor.test(x = covid$Expenditure, y = covid$cases, method = "pearson")
```

```{r}
plot(covid$cases, covid$Expenditure, 
     xlab="Expenditure", 
     ylab="Cases")
```

2.DEADS
```{r}
cor.test(x = covid$Expenditure, y = covid$deads, method = "pearson")
```

```{r}
plot(covid$GovernmentHealthExp.P.C, covid$deads, 
     xlab="Expenditure", 
     ylab="Deads")
```

3.MORTALITY
```{r}
cor.test(x = covid$Expenditure, y = covid$mortality, method = "pearson")
```

```{r}
plot(covid$Expenditure, covid$mortality, 
     xlab="Expenditure", 
     ylab="mortality")
```


4.DEADS PER 100K
```{r}
cor.test(x = covid$Expenditure, y = covid$deadsPER100k, method = "pearson")
```

```{r}
plot(covid$deadsPER100k, covid$Expenditure, 
     xlab="Expenditure", 
     ylab="Deads per 100k")
```

5. CASES PER 100K
```{r}
cor.test(x = covid$Expenditure, y = covid$casesPER100k, method = "pearson")
```

```{r}
plot(covid$Expenditure, covid$casesPER100k, 
     xlab="Revenue", 
     ylab="Cases per 100k")
```

#VARIABLE: surplus-superavit
Cantidad de ingresos que supera los gastos

ANALISIS UNIVARIADO
```{r}
summary(covid$Surplus)
```

ANALSIS BIVARIADO

1.CASES
```{r}
cor.test(x = covid$Surplus, y = covid$cases, method = "pearson")
```

```{r}
plot(covid$cases, covid$Surplus, 
     xlab="Surplus", 
     ylab="Cases")
```

2.DEADS
```{r}
cor.test(x = covid$Surplus, y = covid$deads, method = "pearson")
```

```{r}
plot(covid$Surplus, covid$deads, 
     xlab="Surplus", 
     ylab="Deads")
```

3.MORTALITY
```{r}
cor.test(x = covid$Surplus, y = covid$mortality, method = "pearson")
```

```{r}
plot(covid$Surplus, covid$mortality, 
     xlab="Surplus", 
     ylab="mortality")
```


4.DEADS PER 100K
```{r}
cor.test(x = covid$Surplus, y = covid$deadsPER100k, method = "pearson")
```

```{r}
plot(covid$deadsPER100k, covid$Surplus, 
     xlab="Surplus", 
     ylab="Deads per 100k")
```

5. CASES PER 100K
```{r}
cor.test(x = covid$Surplus, y = covid$casesPER100k, method = "pearson")
```

```{r}
plot(covid$Surplus, covid$casesPER100k, 
     xlab="Surplus", 
     ylab="Cases per 100k")
```

#VARIABLE: Surplus percent - Porcentaje superavit
porcentaje de ingresos que superan los gastos

ANALISIS UNIVARIADO
```{r}
summary(covid$SurplusPercent)
```

ANALSIS BIVARIADO

1.CASES
```{r}
cor.test(x = covid$SurplusPercent, y = covid$cases, method = "pearson")
```

```{r}
plot(covid$cases, covid$SurplusPercent, 
     xlab="Surplus Percent", 
     ylab="Cases")
```

2.DEADS
```{r}
cor.test(x = covid$SurplusPercent, y = covid$deads, method = "pearson")
```

```{r}
plot(covid$SurplusPercent, covid$deads, 
     xlab="Surplus Percent", 
     ylab="Deads")
```

3.MORTALITY
```{r}
cor.test(x = covid$SurplusPercent, y = covid$mortality, method = "pearson")
```

```{r}
plot(covid$SurplusPercent, covid$mortality, 
     xlab="Surplus Percent", 
     ylab="mortality")
```


4.DEADS PER 100K
```{r}
cor.test(x = covid$SurplusPercent, y = covid$deadsPER100k, method = "pearson")
```

```{r}
plot(covid$deadsPER100k, covid$SurplusPercent, 
     xlab="SurplusPercent", 
     ylab="Deads per 100k")
```

5. CASES PER 100K
```{r}
cor.test(x = covid$SurplusPercent, y = covid$casesPER100k, method = "pearson")
```

```{r}
plot(covid$SurplusPercent, covid$casesPER100k, 
     xlab="SurplusPercent", 
     ylab="Cases per 100k")
```


## ADRIANA RAMOS 

### VARIABLE: IHDI

ANALISIS UNIVARIADO
```{r}
summary(covid$ihdi)
```
ANALSIS BIVARIADO

1. Cases

```{r}
cor.test(x = covid$ihdi, y = covid$cases, method = "pearson")
```
```{r}
plot(covid$cases, covid$ihdi, 
     xlab="IHDI", 
     ylab="Cases")
```

2. Deads

```{r}
cor.test(x = covid$ihdi, y = covid$deads, method = "pearson")
```

```{r}
plot(covid$deads, covid$ihdi, 
     xlab="IHDI", 
     ylab="Deads")
```


3. Mortality

```{r}
cor.test(x = covid$ihdi, y = covid$mortality, method = "pearson")
```
```{r}
plot(covid$mortality, covid$ihdi, 
     xlab="IHDI", 
     ylab="Mortality")
```
4. Deads per 100k

```{r}
cor.test(x = covid$ihdi, y = covid$deadsPER100k, method = "pearson")
```

```{r}
plot(covid$deadsPER100k, covid$ihdi, 
     xlab="IHDI", 
     ylab="Deaths per 100k")
```

5. Cases per 100k

```{r}
cor.test(x = covid$ihdi, y = covid$casesPER100k, method = "pearson")
```

```{r}
plot(covid$casesPER100k, covid$ihdi, 
     xlab="IHDI", 
     ylab="Cases per 100k")
```
### VARIABLE: HDI

```{r}
summary(covid$hdi)
```

ANALSIS BIVARIADO

1. Cases

```{r}
cor.test(x = covid$hdi, y = covid$cases, method = "pearson")
```

```{r}
plot(covid$cases, covid$hdi, 
     xlab="HDI", 
     ylab="Cases")
```

2. Deads

```{r}
cor.test(x = covid$hdi, y = covid$deads, method = "pearson")
```

```{r}
plot(covid$deads, covid$hdi, 
     xlab="HDI", 
     ylab="Deaths")
```

3. Mortality

```{r}
cor.test(x = covid$hdi, y = covid$mortality, method = "pearson")
```

```{r}
plot(covid$mortality, covid$hdi, 
     xlab="HDI", 
     ylab="Mortality")
```

4. Deads per 100k

```{r}
cor.test(x = covid$hdi, y = covid$deadsPER100k, method = "pearson")
```

```{r}
plot(covid$deadsPER100k, covid$hdi, 
     xlab="HDI", 
     ylab="Deaths per 100k")
```

5. Cases per 100k

```{r}
cor.test(x = covid$hdi, y = covid$casesPER100k, method = "pearson")
```

```{r}
plot(covid$casesPER100k, covid$hdi, 
     xlab="HDI", 
     ylab="Cases per 100k")
```

### VARIABLE: PBI
ANALISIS UNIVARIADO

```{r}
summary(covid$pbi)
```

ANALISIS BIVARIADO

1. Cases

```{r}
cor.test(x = covid$pbi, y = covid$cases, method = "pearson")
```

```{r}
plot(covid$cases, covid$pbi, 
     xlab="PBI", 
     ylab="Cases")

```

2. Deads

```{r}
cor.test(x = covid$pbi, y = covid$deads, method = "pearson")
```

```{r}
plot(covid$deads, covid$pbi, 
     xlab="PBI", 
     ylab="Deaths")
```


3. Mortality

```{r}
cor.test(x = covid$pbi, y = covid$mortality, method = "pearson")
```

```{r}
plot(covid$mortality, covid$pbi, 
     xlab="PBI", 
     ylab="Mortality")
```


4. Deads per 100k

```{r}
cor.test(x = covid$pbi, y = covid$deadsPER100k, method = "pearson")
```

```{r}
plot(covid$deadsPER100k, covid$pbi, 
     xlab="PBI", 
     ylab="Deaths per 100k")
```


5. Cases per 100k

```{r}
cor.test(x = covid$pbi, y = covid$casesPER100k, method = "pearson")
```

```{r}
plot(covid$casesPER100k, covid$pbi, 
     xlab="PBI", 
     ylab="Cases per 100k")
```


### VARIABLE: Corporate Percent
ANALISIS UNIVARIADO

```{r}
summary(covid$CorporatePercent)
```

ANALISIS BIVARIADO

1. Cases

```{r}
cor.test(x = covid$CorporatePercent, y = covid$cases, method = "pearson")
```

```{r}
plot(covid$cases, covid$CorporatePercent, 
     xlab="Corporate tax percent", 
     ylab="Cases")

```

2. Deads

```{r}
cor.test(x = covid$CorporatePercent, y = covid$deads, method = "pearson")
```

```{r}
plot(covid$deads, covid$CorporatePercent, 
     xlab="Corporate tax percent", 
     ylab="Deaths")
```


3. Mortality

```{r}
cor.test(x = covid$CorporatePercent, y = covid$mortality, method = "pearson")
```

```{r}
plot(covid$mortality, covid$CorporatePercent, 
     xlab="Corporate tax percent", 
     ylab="Mortality")
```


4. Deads per 100k

```{r}
cor.test(x = covid$CorporatePercent, y = covid$deadsPER100k, method = "pearson")
```

```{r}
plot(covid$deadsPER100k, covid$CorporatePercent, 
     xlab="Corporate tax percent", 
     ylab="Deaths per 100k")
```


5. Cases per 100k

```{r}
cor.test(x = covid$CorporatePercent, y = covid$casesPER100k, method = "pearson")
```

```{r}
plot(covid$casesPER100k, covid$CorporatePercent, 
     xlab="Corporate tax percent", 
     ylab="Cases per 100k")
```



MANUEL MAYAUTE
VARIABLE: IncomeHighPercent

ANALISIS UNIVARIADO
```{r}
summary(covid$IncomeHighPercent)
```

ANALSIS BIVARIADO

```{r}
covid[c(20:23)]=lapply(covid[c(2:13)], as.numeric)

```

1.CASES
```{r}
cor.test(x = covid$IncomeHighPercent, y = covid$cases, method = "pearson")
```

```{r}
plot(covid$cases, covid$IncomeHighPercent, 
     xlab="IncomeHighPercent", 
     ylab="Cases")
```

2.DEADS
```{r}
cor.test(x = covid$IncomeHighPercent, y = covid$deads, method = "pearson")
```

```{r}
plot(covid$IncomeHighPercent, covid$deads, 
     xlab="Income", 
     ylab="Deads")
```

3.MORTALITY
```{r}
cor.test(x = covid$IncomeHighPercent, y = covid$mortality, method = "pearson")
```

```{r}
plot(covid$IncomeHighPercent, covid$mortality, 
     xlab="Income", 
     ylab="mortality")
```


4.DEADS PER 100K
```{r}
cor.test(x = covid$IncomeHighPercent, y = covid$deadsPER100k, method = "pearson")
```

```{r}
plot(covid$deadsPER100k, covid$IncomeHighPercent, 
     xlab="Income", 
     ylab="Deads per 100k")
```

5. CASES PER 100K
```{r}
cor.test(x = covid$IncomeHighPercent, y = covid$casesPER100k, method = "pearson")
```

```{r}
plot(covid$IncomeHighPercent, covid$casesPER100k, 
     xlab="Income", 
     ylab="Cases per 100k")
```


dr density
#VARIABLE: doctors_density
Densidad de doctores

ANALISIS UNIVARIADO
```{r}
summary(covid$doctors_density)
```

ANALISIS BIVARIADO

1.CASES
```{r}
cor.test(x = covid$doctors_density, y = covid$cases, method = "pearson")
```

```{r}
plot(covid$cases, covid$doctors_density, 
     xlab="Doctors", 
     ylab="Cases")
```

2.DEADS
```{r}
cor.test(x = covid$doctors_density, y = covid$deads, method = "pearson")
```

```{r}
plot(covid$doctors_density, covid$deads, 
     xlab="Doctors", 
     ylab="Deads")
```

3.MORTALITY
```{r}
cor.test(x = covid$doctors_density, y = covid$mortality, method = "pearson")
```

```{r}
plot(covid$doctors_density, covid$mortality, 
     xlab="Doctors", 
     ylab="mortality")
```


4.DEADS PER 100K
```{r}
cor.test(x = covid$doctors_density, y = covid$deadsPER100k, method = "pearson")
```

```{r}
plot(covid$deadsPER100k, covid$doctors_density, 
     xlab="Doctors", 
     ylab="Deads per 100k")
```

5. CASES PER 100K
```{r}
cor.test(x = covid$doctors_density, y = covid$casesPER100k, method = "pearson")
```

```{r}
plot(covid$doctors_density, covid$casesPER100k, 
     xlab="Doctors", 
     ylab="Cases per 100k")
```

#VARIABLE: vat percent
porcentaje de ingresos que superan los gastos

ANALISIS UNIVARIADO
```{r}
summary(covid$VATpercent)
```

ANALSIS BIVARIADO

1.CASES
```{r}
cor.test(x = covid$VATpercent, y = covid$cases, method = "pearson")
```

```{r}
plot(covid$cases, covid$VATpercent, 
     xlab="vat Percent", 
     ylab="Cases")
```

2.DEADS
```{r}
cor.test(x = covid$VATpercent, y = covid$deads, method = "pearson")
```

```{r}
plot(covid$VATpercent, covid$deads, 
     xlab="vat", 
     ylab="Deads")
```

3.MORTALITY
```{r}
cor.test(x = covid$VATpercent, y = covid$mortality, method = "pearson")
```

```{r}
plot(covid$VATpercent, covid$mortality, 
     xlab="vat Percent", 
     ylab="mortality")
```


4.DEADS PER 100K
```{r}
cor.test(x = covid$VATpercent, y = covid$deadsPER100k, method = "pearson")
```

```{r}
plot(covid$deadsPER100k, covid$VATPercent, 
     xlab="vatPercent", 
     ylab="Deads per 100k")
```


```{r}
#5. CASES PER 100K

cor.test(x = covid$VATpercent, y = covid$casesPER100k, method = "pearson")
```

```{r}
plot(covid$VATpercent, covid$casesPER100k, 
     xlab="VATPercent", 
     ylab="Cases per 100k")
```

#VARIABLE: nursing_density
Densidad de doctores
ANALISIS UNIVARIADO

```{r}

summary(covid$nursing_density)
```

ANALSIS BIVARIADO

1.CASES
```{r}
cor.test(x = covid$nursing_density, y = covid$cases, method = "pearson")
```

```{r}
plot(covid$cases, covid$nursing_density, 
     xlab="nursing density", 
     ylab="Cases")
```

2.DEADS
```{r}
cor.test(x = covid$nursing_density, y = covid$deads, method = "pearson")
```

```{r}
plot(covid$nursing_density, covid$deads, 
     xlab="nursing", 
     ylab="Deads")
```

3.MORTALITY

```{r}
cor.test(x = covid$nursing_density, y = covid$mortality, method = "pearson")
```

```{r}
plot(covid$nursing_density, covid$mortality, 
     xlab="nursing", 
     ylab="mortality")
```


4.DEADS PER 100K
```{r}
cor.test(x = covid$nursing_density, y = covid$deadsPER100k, method = "pearson")
```

```{r}
plot(covid$deadsPER100k, covid$nursing_density, 
     xlab="Doctors", 
     ylab="Deads per 100k")
```

5. CASES PER 100K
```{r}
cor.test(x = covid$nursing_density, y = covid$casesPER100k, method = "pearson")
```

```{r}
plot(covid$nursing_density, covid$casesPER100k, 
     xlab="nursing density", 
     ylab="Cases per 100k")
```





